Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-25 ms.tex

\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data.
The GAIA DR2 parallax of 618 $\pm$ 12 pc can be used with the bolometric flux and effective temperature to estimate the stellar radius \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
We estimate a radius of 0.7 R$_\odot$, which is consistent with a main-sequence star.

@@

As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
\citet{croll2015starspots} calculate that unocculted spots

>>>>

\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 pc.
We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model.
We also assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.

@@

As discussed in Section \ref{sec:intro}, \citet{kawahara2013starspots} first noted an anti-correlation between the transit depths of \sha\ and the flux of its host star.
This correlation implies that the planet disintegration is regulated by the high energy radiation or magnetic energy associated with star spots and that the planet's passage over the spot can increase the disintegration activity.
\citet{croll2015starspots} confirm this anti-correlation but offer a different explanation: occulted dark spots on the stellar surface can decrease the transit depth because the planetary debris extincts less total starlight.
If there is a localized grouping of spots that the planet's transit chord passes through, this could create a positive correlation of transit depth with stellar flux.
\citet{croll2015starspots} note that the spots could have a complicated distribution and that a separate set of spots on the other side of the star could dominate the overall light curve rotational modulation but be at a different latitude from the transit chord, thus creating an anti-correlation between transit depth and stellar flux.
\citet{croll2015starspots} calculate that unocculted spots 
>>>>>>> 5cf2b3b9d0cb4ff5d079f02e7c26986a56147bb5
